The \frb\ Campaign: Multi-Observatory Radio Burst and Implications for the FRB Population

### 2017-02-06 repeater-vladata.tex
clean up for tex

\subsection{Emission Physics and Burst Energetics}
The refined analysis shows that \frb\ has even higher isotropic energies than previously reported, reaching energies $E_{\rm{max}}\approx10^{40}$\ erg. We now know that \frb\ is detectable with the VLA out to $z=0.7$\ and much farther with Arecibo. \frb\ has isotropic energies orders of magnitude higher than the strongest Crab pulsar pulses ($\sim10^{35}\ erg) and comparable brightness temperatures \citep[$T_b^{\rm{Crab}}\sim10^{41}$~K versus $T_b^{\rm{FRB 121102}}\sim10^{38}$~K]{2003Natur.422..141H,2014PhRvD..89j3009K}. While this emission is coherent and strongly beamed \citep{2016Natur.531..202S, WEIRD}, the energy scale is still larger than any Galactic class of fast radio transient and requires either a new process or dramatic scaling of known emission processes \citep{2016MNRAS.462..941L, 2016MNRAS.457..232C}.

Propagation effects (e.g., scintillation, scattering) can also modify the radio signal in a variety of ways and the duration of the emission in the source frame is not known \citep{2016arXiv160505890C}. \citet{CORDES} describe a model where plasma lensing near the source of an FRB can magnify radio emission by orders of mangitude. That model argues that the simultaneous appearance of a burst from 1.2 to 3.5~GHz requires a lens with the focal frequency be $\gtrsim 3.5$~GHz. This gives a constraint on the combination $\frac{\rm DM_0}{a_{\rm AU}^2} \frac{d_{sl}d_{lo}/d_{so}}{1\, \rm kpc} \gtrsim (3.5 / 39.1)^2$, where $DM_0$, $a$, and $d_*$\ are the electron column density of the lens, size of the lens, and lensing distances, respectively. A lens placed at $d_{sl}\approx1$~kpc is consistent with typical properties of the interstellar medium. Lenses that are influenced by the source would be much nearer to the source $d_{\sl} \ll 1$~kpc, requiring large values of ${\rm DM_0 / a_{\rm AU}^2$.

@@

Assuming that the \frb\ energy distribution is typical of FRBs, we can use it to simulate FRB populations and compare their flux distributions to the observed distribution. First, we assume an FRB population that is uniformly distributed in space from redshifts $z1$\ to $z2$. For each FRB source, we sample one FRB burst luminosity from a powerlaw distribution and calculate its flux.
%(uniform for energies from $10^{38}$\ to $10^{40}$; \S \ref{sec:disn} 
We sample 100 such populations and measure 95\% bounds on the distribution of cumulative flux distribution index.
We can show that the flux distribution powerlaw is --1.5 for a standard candle-like luminosity distribution at low redshift. For distributions out to $z2>1$, the distribution flattens slightly ($sim0.3$ in the index) due to cosmological space distortions.
For a large ($N\sim2000) population of such bursts, we select the brightest $M\sim20$\ to represent the flux-limited FRB sample of known FRBs...
The tail of this distribution selects for extrema, such cut-offs in the intrinsic distribution or propagation effects \citep{2015MNRAS.451.3278M, CORDES}. 
We then fit the flux distribution of those $M$\ events with a powerlaw.

>>>>

\subsection{Emission Physics and Burst Energetics}
The refined analysis shows that \frb\ has even higher isotropic energies than previously reported, reaching energies $E_{\rm{max}}\approx10^{40}$\ erg. We now know that \frb\ is detectable with the VLA out to $z=0.7$\ and much farther with Arecibo. \frb\ has isotropic energies orders of magnitude higher than the strongest Crab pulsar pulses ($\sim10^{35}$~erg) and comparable brightness temperatures \citep[$T_b^{\rm{Crab}}\sim10^{41}$~K versus $T_b^{\rm{FRB 121102}}\sim10^{38}$~K;][]{2003Natur.422..141H,2014PhRvD..89j3009K}. While this emission is coherent and strongly beamed \citep{2016Natur.531..202S, WEIRD}, the energy scale is still larger than any Galactic class of fast radio transient and requires either a new process or dramatic scaling of known emission processes \citep{2016MNRAS.462..941L, 2016MNRAS.457..232C}.

Propagation effects (e.g., scintillation, scattering) can also modify the radio signal in a variety of ways and the duration of the emission in the source frame is not known \citep{2016arXiv160505890C}. \citet{CORDES} describe a model where plasma lensing near the source of an FRB can magnify radio emission by orders of mangitude. That model argues that the simultaneous appearance of a burst from 1.2 to 3.5~GHz requires a lens with the focal frequency be $\gtrsim 3.5$~GHz. This gives a constraint on the combination 
$$\frac{\rm DM_0}{a_{\rm AU}^2} \frac{d_{sl}d_{lo}/d_{so}}{1\, \rm kpc} \gtrsim (3.5 / 39.1)^2$$
where $DM_0$, $a$, and $d_*$\ are the electron column density of the lens, size of the lens, and lensing distances, respectively. A lens placed at $d_{sl}\approx1$~kpc is consistent with typical properties of the interstellar medium. Lenses that are influenced by the source would be much nearer to the source $d_{\sl} \ll 1$~kpc, requiring large values of $\frac{\rm DM_0}{a_{\rm AU}^2}$.

@@

Assuming that the \frb\ energy distribution is typical of FRBs, we can use it to simulate FRB populations and compare their flux distributions to the observed distribution. First, we assume an FRB population that is uniformly distributed in space from redshifts $z1$\ to $z2$. For each FRB source, we sample one FRB burst luminosity from a powerlaw distribution and calculate its flux.
%(uniform for energies from $10^{38}$\ to $10^{40}$; \S \ref{sec:disn} 
We sample 100 such populations and measure 95\% bounds on the distribution of cumulative flux distribution index.
We can show that the flux distribution powerlaw is --1.5 for a standard candle-like luminosity distribution at low redshift. For distributions out to $z2>1$, the distribution flattens slightly ($sim0.3$ in the index) due to cosmological space distortions.
For a large ($N\sim2000$) population of such bursts, we select the brightest $M\sim20$\ to represent the flux-limited FRB sample of known FRBs...
The tail of this distribution selects for extrema, such cut-offs in the intrinsic distribution or propagation effects \citep{2015MNRAS.451.3278M, CORDES}. 
We then fit the flux distribution of those $M$\ events with a powerlaw.
